Multilevel computation of glacier geometry \\ from Stokes dynamics

### 2021-05-31 paper/msg.tex
Add notes to self.

@@

Assume $\Omega \subset \RR^d$ is polygonal and suppose $\mathcal{T}$ is a triangulation of $\Omega$.  (If $d=1$ then instead $\mathcal{T}$ denotes an interval decomposition of $\Omega$.)  Based on low expected regularity at the ice margin, we will represent surface elevations $s\in \mathcal{K}$ using the $P_1$ finite element (FE) space
\begin{equation}
\mathcal{V}^h = \{s \in C^0(\Omega) : s|_T \text{ is linear if } T \in \mathcal{T}\} \subset W^{1,\qq}(\Omega).
\end{equation}
Note \cite{JouvetBueler2012} makes the same FE choice for the corresponding shallow problem.

@@

>>>>

FIXME TALK ABOUT IDO.  1 FORM IN SIA CASE. 2 LINEARIZATION DENSE.  3 SPECTRUM OF IDO DETERMINES STABILITY OF EXPLICIT TIME-STEPPING. 4 DIAGONAL OF IDO UNKNOWN BUT POSITIVE?

@@

Assume $\Omega \subset \RR^d$ is polygonal and that $\mathcal{T}$ is a triangulation of $\Omega$.  (If $d=1$ then instead $\mathcal{T}$ denotes an interval decomposition of $\Omega$.)  Based on low expected regularity at the ice margin, we will represent surface elevations $s\in \mathcal{K}$ using the $P_1$ finite element (FE) space
\begin{equation}
\mathcal{V}^h = \{s \in C^0(\Omega) : s|_T \text{ is linear if } T \in \mathcal{T}\} \subset W^{1,\qq}(\Omega).
\end{equation}
Note \cite{JouvetBueler2012} makes the same FE choice for the corresponding shallow problem.

@@

FIXME SMOOTHER POSSIBILITIES.  1 COLORING (PSEUDO-COLORING WITH LATERAL SEPARATION OF A FEW ICE THICKNESSES).  2 PATCH-TYPE WHICH SOLVE LOW-DIMENSIONAL VI.
